---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# edgr

<!-- badges: start -->
<!-- badges: end -->

The goal of {edgr} is to help you analyze 10-K filings from the SEC's EDGAR database.

## Installation

You can install the development version of {edgr} from [GitHub](https://github.com/) with:

```{r, message=FALSE, warning=FALSE, eval=FALSE}
# install.packages("remotes")
remotes::install_github("m-pilarski/edgr")
```

## Example

```{r, cache=FALSE, message=FALSE}
library(tidyverse)
library(edgr)

# Set the number of workers for parallel processing
options("edgr.n_workers"=1)
# Set the number of workers for parallel processing
options("edgr.user_agent"=paste0(
  "Mozilla/5.0 (iPhone; CPU iPhone OS 17_6_1 like Mac OS X) ",
  "AppleWebKit/605.1.15 (KHTML, like Gecko) Version/17.6 Mobile/15E148 ",
  "Safari/604.1"
))
```

Get the document index files for the years 2020 to 2023

```{r, cache=TRUE}
doc_index_data <- gather_doc_index_data(
  .years=2010:2015, .data_dir=fs::dir_create(here::here("README_files/data/"))
)

doc_index_data
```

{edgr} includes a scraped dataset `com_indu_data` that includes information on companies' sectors.

```{r}
com_indu_data

com_indu_data |> distinct(indu_sic, indu_title)
```

You can use it to get the CIKs for companies from sectors that are relevant for your analysis. 

```{r, cache=TRUE}
com_indu_health_data <- com_indu_data |> filter(
  str_detect(indu_sic, "^80\\d\\d$")
)

com_indu_health_data

com_indu_health_data |> distinct(indu_sic, indu_title)
```

Collect and clean the 10-Ks for the selected companies and years.

```{r}
doc_parse_data <- doc_index_data |> 
  # keep only companies from the relevant sectors
  semi_join(com_indu_health_data, by=join_by(com_cik)) |>
  # download raw filings from the SEC
  gather_doc_raw_data() |> 
  # parse the raw filings and store body and head into separate files
  gather_doc_parse_data()
```

The processed data is now stored in the directory that you set above.

```{r}
fs::dir_info(get_data_dir(doc_parse_data), recurse=FALSE)
```

```{r, warning=FALSE}
doc_parse_data |> 
  slice_sample(n=10) |> 
  gather_doc_stat_body_data(function(.doc_parse){
    # .doc_parse <<- .doc_parse; stop()
    .doc_parse |> 
      prep_doc_clean_body_string() |> 
      sentimentr::get_sentences() |> 
      sentimentr::sentiment() |> 
      summarize(
        sentence_count = n(), 
        word_count = sum(word_count),
        sentiment_mean = mean(sentiment),
        sentiment_sd = sd(sentiment)
      ) |> 
      as_tibble()
  }, .n_workers=1) |> 
  glimpse()
```



# License

{edgr} is distributed under the MIT License. See the [LICENSE](./LICENSE) file for details.
