---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# edgr

<!-- badges: start -->
<!-- badges: end -->

The goal of {edgr} is to help you analyze 10-K filings from the SEC's EDGAR database.

## Installation

You can install the development version of {edgr} from [GitHub](https://github.com/) with:

```{r, message=FALSE, warning=FALSE}
# install.packages("remotes")
remotes::install_github("m-pilarski/edgr")
```

## Example

```{r, cache=FALSE, message=FALSE}
library(tidyverse)
library(edgr)

# Set the number of workers for parallel processing
options("edgr.n_workers"=3)
```

Get the document index files for the years 2020 to 2023

```{r, cache=TRUE}
doc_index_data <- gather_doc_index_data(
  .years=2021:2023, .data_dir=fs::dir_create(here::here("README_files/data/"))
)

doc_index_data
```

{edgr} includes a scraped dataset `com_indu_data` that includes information on companies' sectors.

```{r}
com_indu_data

com_indu_data |> distinct(indu_sic, indu_title)
```

You can use it to get the CIKs for companies from sectors that are relevant for your analysis.

```{r, cache=TRUE}
com_indu_health_data <- com_indu_data |> filter(
  str_detect(indu_sic, "^80\\d\\d$")
)

com_indu_health_data

com_indu_health_data |> distinct(indu_sic, indu_title)
```

Collect and clean the 10-Ks for the selected companies and years.

```{r}
doc_clean_data <- doc_index_data |> 
  # keep only companies from the relevant sectors
  semi_join(com_indu_health_data, by=join_by(com_cik)) |>
  # for this example: only use the first 10 of the matched companies
  filter(com_cik %in% unique(com_cik)[1:10]) |> 
  gather_doc_clean_data()
```

The processed data is now stored in the directory that you set above.

```{r}
fs::dir_tree(doc_clean_data %@% "data_dir", recurse=TRUE)
```


# License

{edgr} is distributed under the MIT License. See the [LICENSE](./LICENSE) file for details.
